Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2021-10-14 manuscript/manuscript.tex
code cleaning

Model-based forecasts, which have played an important role in shaping public policy throughout the Covid-19 pandemic, represent an implicit combination of model assumptions and the researcher's subjective opinion. This work explicitly separates human opinion and model-derived insights to assess and compare the relative strengths and weaknesses of both approaches. We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers (``crowd forecasts''), against predictions from two semi-mechanistic epidemiological models. In addition, we compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions (``Hub ensemble''). We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 89\%), but not when predicting deaths (rel. WIS 126\%). Crowd forecasts were severely overconfident (55\% and 75\% coverage of the 95\% prediction intervals for cases and deaths, respectively) when compared to model-based predictions. Performance of the untuned models deteriorated quickly with increasing forecast horizon when assumptions were no longer met (rel. WIS \textgreater{} 164\% for all four week ahead predictions).

@@

Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza {[}CITATION{]}, dengue fever {[}Citation{]}, ebola {[}Citation{]}, chikungunya and now COVID-19 {[}Citation{]}. The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models (CITE e.g UK, US and German/Polish papers). Yet it has been difficult to discern which factors lead to good COVID-19 forecasts. Answering this question is complicated by the varying and generally unobserved degree of manual expert intervention. Model-based forecasts usually represent an implicit combination of human judgement and model-derived insights, in the sense that forecasts have been generated with the help of epidemiological or statistical models, but throughout the process were manually changed and adjusted according to the researchers' judgement.

@@

In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts and model-based predictions.

@@

We created a crowd-sourced forecast (``crowd forecast''), elicited from participants through a web application {[}Citation{]}, as well as two semi-mechanistic models (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology. Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (CITATION). All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (N. Bosse et al.~2020). This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub. Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the Forecast Hub.

@@

Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub (J. Bracher et al.~2021). Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) (``Download Historical Data (to 14 December 2020) on the Daily Number of New Reported COVID-19 Cases and Deaths Worldwide'' 2020). After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (``RKI - Coronavirus SARS-CoV-2 - Aktueller Lage-/Situationsbericht Des RKI Zu COVID-19'' n.d.). These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November (``Rozbieżności w statystykach koronawirusa. 22 tys. przypadków będą doliczone do ogólnej liczby wyników'' 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g.~in Germany from the 11th of November on (Ärzteblatt 2020)).

@@

Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (\url{https://cmmid-lshtm.shinyapps.io/crowd-forecast/}). Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday. The application was built using the shiny and golem R packages (Chang et al.~2021; Fay et al.~2021) and is available in the crowdforecastr R package (N. I. Bosse et al.~2020). To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values. The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.~as \texttt{sd(c(log(value4)\ -\ log(value3),\ log(value3)\ -\ log(value2),\ ...))}).
Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (``COVID-19 Data Explorer'' n.d.). These data included e.g.~notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.

@@

We used two models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al.~2020). The first of these models, here called ``renewal model,'' used the renewal equation (Fraser 2007) to predict reported cases and deaths. It estimated the effective reproduction number \(R_t\) (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times \(R_t\). \(R_t\) was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in infections. The \(R_t\) value which was carried forward was slightly changed on November 9th 2020, where before that date the last `reliable' \(R_t\) estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) \(R_t\) estimate made on the actual forecast date was used. Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al.~2020; DOI n.d.; ``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England \textbar{} medRxiv'' n.d.) to model the time between infection and report date or death. The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that \(R_t\) was forecast once from reported cases and once from reported deaths. Death forecasts from the renewal model were therefore not informed by past cases. One submission of the renewal model on December 28th 2020 was belated and therefore not included in the official Forecast hub ensemble.

The second model (``convolution model'') was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses). The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model. The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio). Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al.~2020). Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August. All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately. More details are available in the supplementary information.

@@

For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions (J. Bracher et al.~2021). Forecasts for cases were scored using the full period from October 2020 until March 2021. To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available. To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) where scored only over the later period where are forecasts were available (see Section \ref{sensitivity-analysis} in the SI). Results remained broadly unchanged.

Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher et al.~2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals. The WIS is a proper scoring rule (CITE GNEITING) and can be understood as a generalisation of the absolute error to quantile-based forecasts. It can be decomposed into three separate penalties: forecast spread (i.e.~uncertainty of forecasts), over-prediction and under-prediction - lower values are always better. While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts. The bias metric we use captures how much probability mass of the forecast was above or below the true value and therefore represents a general tendency to over- or under-predict in relative terms. It is bound between -1 (all quantiles of the predictive distribution are below the observed value) and 1 (all quantiles are above the observed value). Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.~how many observed values fall inside all 50\% prediction intervals). Scoring metrics are explained in more detail in Table \ref{tab:scoring-metrics} in the SI. All scores were calculated using the \texttt{scoringutils} R package (N. Bosse 2020).

@@

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \ref{fig:agg-performance-all}A) and locations (Figure \ref{fig:performance-locations-rel}A). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 100\%) was 89\% for crowd forecasts and 140\% for the renewal model (Table \ref{tab:score-table-2}). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}). Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}, as well as the highest standard deviation of WIS values (relative WIS sd 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.

@@

Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts. However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (Cite US Hub, cite Seb SPI-M), or exclusively on human forecasts (e.g.~cite Tetlock, cite Grecchia, cite McAndrew). In contrast, we directly compared human and model-based forecasts. This is similar to the approach taken by Farrow et al., but extends it in several ways. While Farrow et al.~only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence. In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight. In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (J. Bracher et al.~2021; E. Y. Cramer et al.~2021; S. Funk et al.~2020).

@@

where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\) and \(I'_t\) are the unadjusted infections defined above. This adjustment is based on that implemented in the \texttt{epidemia} R package (Scott et al. (2020), cite (\textbf{bhatt202?})).

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

Model-based forecasts, which have played an important role in shaping public policy throughout the Covid-19 pandemic, represent an implicit combination of model assumptions and the researcher's subjective opinion. This work explicitly separates human opinion and model-derived insights to assess and compare the relative strengths and weaknesses of both approaches. We compared purely opinion-derived forecasts of cases and deaths from COVID-19 in Germany and Poland, elicited from researchers and volunteers (``crowd forecasts''), against predictions from two semi-mechanistic epidemiological models. In addition, we compared these forecasts against an ensemble of model-based, but expert-tuned, forecasts, submitted to the German and Polish Forecast Hub by other research institutions (``Hub ensemble''). We found an ensemble of crowd-sourced predictions to outperform all other methods when predicting cases (Weighted Interval Score relative to the Hub ensemble at a two-week horizon: 0.89), but not when predicting deaths (rel. WIS 1.26). Crowd forecasts were severely overconfident (55\% and 75\% coverage of the 90\% prediction intervals for cases and deaths, respectively) when compared to model-based predictions. Performance of the untuned models deteriorated quickly with increasing forecast horizon when assumptions were no longer met (rel. WIS \textgreater{} 1.64 for all four week ahead predictions).

@@

Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza (e.g. McGowan et al. 2019; \textbf{reichCollaborativeMultiyearMultimodel2019?}; Shaman and Karspeck 2012; \textbf{biggerstaffResultsCentersDisease2016?}), dengue fever (e.g. Johansson et al. 2019; Yamana, Kandula, and Shaman 2016; Colón-González et al. 2021), ebola (e.g. Viboud et al. 2018; Funk et al. 2019), chikungunya (e.g. Del Valle et al. 2018; Farrow et al. 2017) and now COVID-19 (e.g. Funk et al. 2020; \textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al. 2021; Bracher, Wolffram, et al. 2021; Hub 2021). The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models. Yet it has been difficult to discern which factors lead to good COVID-19 forecasts. Answering this question is complicated by the varying and generally unobserved degree of manual expert intervention. Model-based forecasts usually represent an implicit combination of human judgement and model-derived insights, in the sense that forecasts have been generated with the help of epidemiological or statistical models, but throughout the process were manually changed and adjusted according to the researchers' judgement.

@@

In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses. To allow for a direct comparison on an equal footing we employ a novel approach that elicits full probabilistic forecasts (Held, Meyer, and Bracher 2017) from participants, rather than constructing a predictive distribution from individual point predictions.

@@

We created a crowd-sourced forecast (``crowd forecast''), elicited from participants through a web application (N. I. Bosse et al. 2020), as well as two semi-mechanistic models (``renewal model'' and ``convolution model'') informed by basic assumptions about COVID-19 epidemiology. Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (Bracher, Wolffram, et al. 2021). All code and tools necessary to generate the forecasts and make a forecast submission are available in the \texttt{covid.german.forecasts} R package (N. Bosse et al. 2020). This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub. Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the Forecast Hub.

@@

Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub. Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) ({``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide''} 2020). After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period ({``{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} Des {RKI} Zu {COVID}-19''} n.d.). These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November ({``Rozbieżności w statystykach koronawirusa. 22 tys. przypadków będą doliczone do ogólnej liczby wyników''} 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g.~in Germany from the 11th of November on (Ärzteblatt 2020)).

@@

Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application (\url{https://cmmid-lshtm.shinyapps.io/crowd-forecast/}). Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday. The application was built using the shiny and golem R packages (Fay et al. 2021; Chang et al. 2021) and is available in the \texttt{crowdforecastr} R package (N. I. Bosse et al. 2020). To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values. The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e.~as \texttt{sd(c(log(value4)\ -\ log(value3),\ log(value3)\ -\ log(value2),\ ...))}).
Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from ({``{COVID}-19 {Data Explorer}''} n.d.). These data included e.g.~notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.

@@

We used two models from the \texttt{EpiNow2} R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al. 2020). The first of these models, here called ``renewal model,'' used the renewal equation (Fraser 2007) to predict reported cases and deaths. It estimated the effective reproduction number \(R_t\) (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times \(R_t\). \(R_t\) was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in infections. The \(R_t\) value which was carried forward was slightly changed on November 9th 2020, where before that date the last `reliable' \(R_t\) estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) \(R_t\) estimate made on the actual forecast date was used. Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al. 2020; DOI n.d.; {``Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the {Covid}-19 Outbreak in {England} \textbar{} {medRxiv}''} n.d.) to model the time between infection and report date or death. The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that \(R_t\) was forecast once from reported cases and once from reported deaths. Death forecasts from the renewal model were therefore not informed by past cases. One submission of the renewal model on December 28th 2020 was belated and therefore not included in the official Forecast hub ensemble.

The second model (``convolution model'') was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses). The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model. The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio). Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al. 2020). Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August. All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately. More details are available in the supplementary information.

@@

For the main analysis we focused on two week ahead predictions, as predictions beyond this horizon are often unreliable due to rapidly changing conditions (Bracher, Wolffram, et al. 2021). Forecasts for cases were scored using the full period from October 2020 until March 2021. To ensure comparability between models, all death forecasts were scored using only the period from December 14th on, where all models including the convolution model were available. To ensure robustness of our results we conducted a sensitivity analysis where all forecasts (including cases) where scored only over the later period where are forecasts were available (see Section \ref{sensitivity-analysis} in the SI). Results remained broadly unchanged.

Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Bracher, Ray, et al. 2021), the absolute error, relative bias, and empirical coverage of the 50\% and 90\% prediction intervals. The WIS is a proper scoring rule (Gneiting and Raftery 2007) and can be understood as a generalisation of the absolute error to quantile-based forecasts. It can be decomposed into three separate penalties: forecast spread (i.e.~uncertainty of forecasts), over-prediction and under-prediction - lower values are always better. While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts. The bias metric we use captures how much probability mass of the forecast was above or below the true value and therefore represents a general tendency to over- or under-predict in relative terms. It is bound between -1 (all quantiles of the predictive distribution are below the observed value) and 1 (all quantiles are above the observed value). Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g.~how many observed values fall inside all 50\% prediction intervals). Scoring metrics are explained in more detail in Table \ref{tab:scoring-metrics} in the SI. All scores were calculated using the \texttt{scoringutils} R package (N. Bosse 2020).

@@

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Figure \ref{fig:agg-performance-all}A) and locations (Figure \ref{fig:performance-locations-rel}A). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (Table \ref{tab:score-table-2}). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was right-skewed, and average performance was heavily influenced by outliers (Figure \ref{fig:distribution-scores}). Overall, low variance in forecast performance was closely linked with good mean performance (Figures \ref{fig:agg-performance-all}H and and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers (Figure \ref{fig:distribution-scores}, as well as the highest standard deviation of WIS values (relative WIS sd 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.

@@

Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts. However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (e.g. Funk et al. 2020; \textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al. 2021), or exclusively on human forecasts Recchia, Freeman, and Spiegelhalter (2021). In contrast, we directly compared human and model-based forecasts. This is similar to the approach taken by Farrow et al. (2017), but extends it in several ways. While Farrow et al.~only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence. In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight. In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (\textbf{esteecramerCOVID19ForecastHub2020?}; Cramer et al. 2021; Bracher, Wolffram, et al. 2021; Hub 2021; Funk et al. 2020).

@@

where \(I^c_t = \sum_{s< t} I_s\) are cumulative infections by \(t-1\) and \(I'_t\) are the unadjusted infections defined above. This adjustment is based on that implemented in the \texttt{epidemia} R package (Scott et al. 2020; \textbf{bhatt202?}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-aerzteblattSARSCoV2DiagnostikRKIPasst2020}{}}%
Ärzteblatt, Deutscher Ärzteverlag GmbH, Redaktion Deutsches. 2020. {``SARS-CoV-2-Diagnostik: RKI passt Testempfehlungen an.''} {Deutsches Ärzteblatt}. November 3, 2020. \url{https://www.aerzteblatt.de/nachrichten/118001/SARS-CoV-2-Diagnostik-RKI-passt-Testempfehlungen-an}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-crowdforecastr}{}}%
Bosse, Nikos I., Sam Abbott, EpiForecasts, and Sebastian Funk. 2020. \emph{Crowdforecastr: Eliciting Crowd Forecasts in r Shiny}. \url{https://doi.org/10.5281/zenodo.4618519}.

\leavevmode\vadjust pre{\hypertarget{ref-covidgermanforecasts}{}}%
Bosse, Nikos, Sam Abbott, EpiForecasts, and Sebastian Funk. 2020. \emph{Covid.german.forecasts: Forecasting Covid-19 Related Metrics for the German/Poland Forecast Hub}.

\leavevmode\vadjust pre{\hypertarget{ref-bracherEvaluatingEpidemicForecasts2021}{}}%
Bracher, Johannes, Evan L. Ray, Tilmann Gneiting, and Nicholas G. Reich. 2021. {``Evaluating Epidemic Forecasts in an Interval Format.''} \emph{PLoS Computational Biology} 17 (2): e1008618. \url{https://doi.org/10.1371/journal.pcbi.1008618}.

\leavevmode\vadjust pre{\hypertarget{ref-bracherShorttermForecastingCOVID192021}{}}%
Bracher, Johannes, Daniel Wolffram, J. Deuschel, K. Görgen, J. L. Ketterer, A. Ullrich, S. Abbott, et al. 2021. {``Short-Term Forecasting of {COVID}-19 in {Germany} and {Poland} During the Second Wave -- a Preregistered Study.''} \emph{medRxiv}, January, 2020.12.24.20248826. \url{https://doi.org/10.1101/2020.12.24.20248826}.

\leavevmode\vadjust pre{\hypertarget{ref-shiny}{}}%
Chang, Winston, Joe Cheng, JJ Allaire, Carson Sievert, Barret Schloerke, Yihui Xie, Jeff Allen, Jonathan McPherson, Alan Dipert, and Barbara Borges. 2021. \emph{Shiny: Web Application Framework for r}. \url{https://CRAN.R-project.org/package=shiny}.

\leavevmode\vadjust pre{\hypertarget{ref-colon-gonzalezProbabilisticSeasonalDengue2021}{}}%
Colón-González, Felipe J., Leonardo Soares Bastos, Barbara Hofmann, Alison Hopkin, Quillon Harpham, Tom Crocker, Rosanna Amato, et al. 2021. {``Probabilistic Seasonal Dengue Forecasting in {Vietnam}: A Modelling Study Using Superensembles.''} \emph{PLOS Medicine} 18 (3): e1003542. \url{https://doi.org/10.1371/journal.pmed.1003542}.

\leavevmode\vadjust pre{\hypertarget{ref-COVID19DataExplorer}{}}%
{``{COVID}-19 {Data Explorer}.''} n.d. {Our World in Data}. Accessed May 30, 2021. \url{https://ourworldindata.org/coronavirus-data-explorer}.

\leavevmode\vadjust pre{\hypertarget{ref-cramerEvaluationIndividualEnsemble2021}{}}%
Cramer, Estee, Evan L. Ray, Velma K. Lopez, Johannes Bracher, Andrea Brennen, Alvaro J. Castro Rivadeneira, Aaron Gerding, et al. 2021. {``Evaluation of Individual and Ensemble Probabilistic Forecasts of {COVID}-19 Mortality in the {US}.''} \emph{medRxiv}, February, 2021.02.03.21250974. \url{https://doi.org/10.1101/2021.02.03.21250974}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-delvalleSummaryResults201420152018}{}}%
Del Valle, Sara Y., Benjamin H. McMahon, Jason Asher, Richard Hatchett, Joceline C. Lega, Heidi E. Brown, Mark E. Leany, et al. 2018. {``Summary Results of the 2014-2015 {DARPA Chikungunya} Challenge.''} \emph{BMC Infectious Diseases} 18 (1): 245. \url{https://doi.org/10.1186/s12879-018-3124-7}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-DownloadHistoricalData2020a}{}}%
{``Download Historical Data (to 14 {December} 2020) on the Daily Number of New Reported {COVID}-19 Cases and Deaths Worldwide.''} 2020. {European Centre for Disease Prevention and Control}. December 14, 2020. \url{https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-golem}{}}%
Fay, Colin, Vincent Guyader, Sébastien Rochette, and Cervan Girard. 2021. \emph{Golem: A Framework for Robust Shiny Applications}. \url{https://github.com/ThinkR-open/golem}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-funkShorttermForecastsInform2020}{}}%
Funk, Sebastian, Sam Abbott, B. D. Atkins, M. Baguelin, J. K. Baillie, P. Birrell, J. Blake, et al. 2020. {``Short-Term Forecasts to Inform the Response to the {Covid}-19 Epidemic in the {UK}.''} \emph{medRxiv}, November, 2020.11.11.20220962. \url{https://doi.org/10.1101/2020.11.11.20220962}.

\leavevmode\vadjust pre{\hypertarget{ref-funkAssessingPerformanceRealtime2019}{}}%
Funk, Sebastian, Anton Camacho, Adam J. Kucharski, Rachel Lowe, Rosalind M. Eggo, and W. John Edmunds. 2019. {``Assessing the Performance of Real-Time Epidemic Forecasts: A Case Study of {Ebola} in the {Western Area} Region of {Sierra Leone}, 2014-15.''} \emph{PLOS Computational Biology} 15 (2): e1006785. \url{https://doi.org/10.1371/journal.pcbi.1006785}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-gneiting_strictly_2007}{}}%
Gneiting, Tilmann, and Adrian E Raftery. 2007. {``Strictly Proper Scoring Rules, Prediction, and Estimation.''} \emph{Journal of the American Statistical Association} 102 (477): 359--78. \url{https://doi.org/10.1198/016214506000001437}.

\leavevmode\vadjust pre{\hypertarget{ref-heldProbabilisticForecastingInfectious2017}{}}%
Held, Leonhard, Sebastian Meyer, and Johannes Bracher. 2017. {``Probabilistic Forecasting in Infectious Disease Epidemiology: The 13th {Armitage} Lecture.''} \emph{Statistics in Medicine} 36 (22): 3443--60. \url{https://doi.org/10.1002/sim.7363}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-EuroHub}{}}%
Hub, European COVID-19 Forecast. 2021. {``Forecasts of New Cases and Deaths Due to Covid-19 over the Next Four Weeks in Countries Across Europe and the UK.''} \url{https://covid19forecasthub.eu/}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-johanssonOpenChallengeAdvance2019}{}}%
Johansson, Michael A., Karyn M. Apfeldorf, Scott Dobson, Jason Devita, Anna L. Buczak, Benjamin Baugher, Linda J. Moniz, et al. 2019. {``An Open Challenge to Advance Probabilistic Forecasting for Dengue Epidemics.''} \emph{Proceedings of the National Academy of Sciences} 116 (48): 24268--74. \url{https://doi.org/10.1073/pnas.1909865116}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-mcgowanCollaborativeEffortsForecast2019}{}}%
McGowan, Craig J., Matthew Biggerstaff, Michael Johansson, Karyn M. Apfeldorf, Michal Ben-Nun, Logan Brooks, Matteo Convertino, et al. 2019. {``Collaborative Efforts to Forecast Seasonal Influenza in the {United States}, 2015--2016.''} \emph{Scientific Reports} 9 (1, 1): 683. \url{https://doi.org/10.1038/s41598-018-36361-9}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-RKICoronavirusSARSCoV2a}{}}%
{``{RKI} - {Coronavirus SARS}-{CoV}-2 - {Aktueller Lage}-/{Situationsbericht} Des {RKI} Zu {COVID}-19.''} n.d. Accessed May 30, 2021. \url{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Situationsberichte/Gesamt.html}.

\leavevmode\vadjust pre{\hypertarget{ref-RozbieznosciStatystykachKoronawirusa0100}{}}%
{``Rozbieżności w statystykach koronawirusa. 22 tys. przypadków będą doliczone do ogólnej liczby wyników.''} 16:07:56+0100. 16:07:56+0100. \url{https://forsal.pl/lifestyle/zdrowie/artykuly/8017628,rozbieznosci-w-statystykach-koronawirusa-22-tys-przypadkow-beda-doliczone-do-ogolnej-liczby-wynikow.html}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-shamanForecastingSeasonalOutbreaks2012}{}}%
Shaman, Jeffrey, and Alicia Karspeck. 2012. {``Forecasting Seasonal Outbreaks of Influenza.''} \emph{Proceedings of the National Academy of Sciences} 109 (50): 20425--30. \url{https://doi.org/10.1073/pnas.1208772109}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-viboudRAPIDDEbolaForecasting2018}{}}%
Viboud, Cécile, Kaiyuan Sun, Robert Gaffey, Marco Ajelli, Laura Fumanelli, Stefano Merler, Qian Zhang, Gerardo Chowell, Lone Simonsen, and Alessandro Vespignani. 2018. {``The {RAPIDD} Ebola Forecasting Challenge: Synthesis and Lessons Learnt.''} \emph{Epidemics}, The {RAPIDD Ebola Forecasting Challenge}, 22 (March): 13--21. \url{https://doi.org/10.1016/j.epidem.2017.08.002}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-yamanaSuperensembleForecastsDengue2016}{}}%
Yamana, Teresa K., Sasikiran Kandula, and Jeffrey Shaman. 2016. {``Superensemble Forecasts of Dengue Outbreaks.''} \emph{Journal of The Royal Society Interface} 13 (123): 20160410. \url{https://doi.org/10.1098/rsif.2016.0410}.
